Genetic algorithms snake game

### 2024-05-29 article/article.tex
new changes

The mutation function aims to modify the genome of the offspring. These modifications serve to maintain and introduce diversity in the genetic population, which is crucial for the overall success of the genetic algorithm, and prevents premature convergence.
\begin{quote}
\emph{
    "The role of mutation in GAs has been that of restoring lost or unexplored genetic material into the population to prevent the premature convergence of the GA to suboptimal solutions."
    }
    \cite{srinvas1994adaptive}
\end{quote}

\subsection{Mutation V.2 Jeff\label{sec:Mutation}}

@@

\section{Analysis\label{sec:Analysis}}
\subsection{Selection\label{sec:Selection}}
\subsection{Fitness\label{sec:Fitness}}
\subsection{Crossover\label{sec:Crossover}}
\subsection{Mutation\label{sec:Mutation}}

>>>>

@@

\section{Analysis\label{sec:Analysis}}
\subsection{Selection\label{sec:Selection}}
\subsection{Fitness\label{sec:Fitness}}
\subsection{Crossover\label{sec:Crossover}}
\subsection{Mutation\label{sec:Mutation}}
single point mutation
